\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-06-19 article.tex
Fixed emphasis on reference list
Started the Intruduction section, and added ideas for the rest of the article

\section*{\centering Abstract}
\begin{em}
  Patterns in ITF Taekwon-Do are defined as a choreographed sequence of
  fundamental movements, which represents an attack or defense towards a
  particular target area or definite action of an attacker, against one or
  several imaginary opponents.

@@

% Approach, Results, Conclusion.

% Introduction
%   - Problem Statement
% Method
%   - Approach
% Results
%   - Tables
%   - Graphs
% Conclusions

@@

\Section{Introduction}

% mer utdypende fra 'abstract', ta med ting fra Right Leg Bias om
% nødvendig osv. sette dette under Previous Work?

@@

% note that Gibb's article includes *all* the patterns

\SubSection{Previous Work}

There are various bibliographic and citation schemes available in
LaTex, but we choose to use the simplest one in this example.

@@

    \bibitem{cyclo:vol1}
      General Choi Hong Hi,
      {\emph Encyclopedia of Taekwon-Do}, Vol. 1, p. 13,
      International Taekwon-Do Federation, 1983.

    \bibitem{rlb}
      M. Gibb,
      {\emph Right Leg Bias in Patterns}, 2009.
      \url{http://visiontkd.co.uk/assetshome/pdf/Rightlegbias.pdf}

>>>>

\section*{\centering Abstract}
\begin{em}
  Patterns in International Taekwon-Do Federation (ITF) are defined as a
  choreographed sequence of fundamental movements, which represents an attack
  or defense towards a particular target area or definite action of an
  attacker, against one or several imaginary opponents.

@@

% Method
%   - Approach
%   - Collecting data
%   - Analysis of data
%   - Uncertainty
% Results
%   - Tables
%   - Graphs
% Conclusions

@@

\Section{Introduction}
A \emph{pattern} is a series of predefined basic elements called fundamental
movements. The \emph{fundamental movements} are attack or defensive techniques
against a specific target area or a predetermined action of an attacker.

Combined in a pattern, the student systematically deals with several imaginary
opponents under various assumptions, using every available attacking and
blocking tool from different directions\cite{cyclo:vol1}.

% incorporate the problem statement within the Introduction instead of using
% its own subsection

\SubSection{Problem Statement}
% pp. 154-155
% given the weight/importance of fundamental movements and patterns in the encyclopedia
% with approximately 3,200 techniques and
%Patterns, therefore,
%are the technical identity of Taekwon-Do.
% The following points should be considered while performing patterns:
%
%   9. Attack and defense techniques should be equally
%      distributed among right and left hands and feet
%
% and
%
% 'using every available attacking and blocking tool from different
% directions..'
%
% and the recent discovery of the right leg bias,
%
% note that Gibb's article includes *all* the patterns

@@

@@

    \bibitem{cyclo:vol1}
      Gen. Choi Hong Hi,
      \emph{Encyclopedia of Taekwon-Do}, Vol. 1, p. 154,
      International Taekwon-Do Federation, 1993.

    \bibitem{rlb}
      M. Gibb,
      \emph{Right Leg Bias in Patterns}, 2009.
      \url{http://visiontkd.co.uk/assetshome/pdf/Rightlegbias.pdf}
